---
title: "Midterm"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Import data from yahoo finance
-----------------------------------------------------------------------------
#There are two primary time series data : xts and zoo
-----------------------------------------------------------------------------
install.packages("quantmod")
```{r}
library(quantmod)
tickers = c("SPY", "QQQ", "EEM", "IWM", "EFA", "TLT", "IYR", "GLD")
getSymbols(tickers, from = "2010-01-01", auto.assign = TRUE)
```
# Getting new data from year 2010 only
```{r}
data = new.env()
getSymbols(tickers, from = "2010-01-01/2010-01-31", env = data , auto.assign = TRUE)
ls(data)
names(data)
head(data$SPY)
```
# Merge Adjusted Price together
```{r}
firmList<-merge(Ad(SPY), Ad(QQQ), Ad(EEM),Ad(IWM), Ad(EFA), Ad(TLT),Ad(IYR),Ad(GLD))
firmList10=firmList['2010']
firmList10
head(firmList10)
colnames(firmList10)<-c("SPY", "QQQ", "EEM","IWM","EFA","TLT","IYR","GLD")
```

# 2.Calculate daily return from year 2010 data

```{r}
firmDaily.ret<-firmList10/lag(firmList10)-1
head(firmDaily.ret)
firmDaily.ret<-firmDaily.ret[-1,]
head(firmDaily.ret)
class(firmDaily.ret)
```

# 3. Calculate weekly return, covariance matrix, and weighted MVP

```{r}
weekly.end <- endpoints(firmList10, on = "weeks")
weekly <- period.apply(firmList10, INDEX = weekly.end, FUN = mean)
head(weekly)
firmWeekly.ret<-weekly/lag(weekly)-1
head(firmWeekly.ret)
firmWeekly.ret<-firmWeekly.ret[-1,]
head(firmWeekly.ret)
class(firmWeekly.ret)
```
#4. Calculate montly return, covariance matrix, and weighted MVP
```{r}
month.end <- endpoints(weekly, on = "months")
monthly <- period.apply(weekly, INDEX = month.end, FUN = mean)
head(monthly)
firmMonthly.ret<-monthly/lag(monthly)-1
head(firmMonthly.ret)
firmMonthly.ret<-firmMonthly.ret[-1,]
head(firmMonthly.ret)
class(firmMonthly.ret)
```
#5. Download Fama/French 3 factors models monthly data, convert to xts file
install.packages('Ecdat')
install.packages('robust')
```{r}
options(digits=5)
FF_data = read.csv("F-F_Research_Data_Factors.CSV")
head(FF_data)
names(FF_data)
attach(FF_data)
library("Ecdat")
library("robust")
stocks=cbind(N=Mkt.RF,SMB,HML)
fit = lm(cbind(Mkt.RF,SMB,HML)~RF)
options(digits=3)
SMB
pairs(cbind(Mkt.RF,SMB,HML))
cor(fit$residuals)
covRob(fit$residuals,cor=F)
cor.test(fit$residuals[,1], fit$residuals[,2])
cor.test(fit$residuals[,1], fit$residuals[,3])
cor.test(fit$residuals[,2], fit$residuals[,3])
pairs(fit$residuals)
n=dim(FF_data)[1]
sigF = as.matrix(var(cbind(Mkt.RF,SMB,HML)))
sigF
bbeta = as.matrix(fit$coef)
bbeta = t( bbeta[-1,])
bbeta
resig2 = apply((fit$resid)^2, 2, sum)/(n-3-1)
resig2 = diag(resig2)
```